Survival Analysis of Questions Posted on iFixit's Answers forum

### 2018-01-28 article/draft1.Rnw
update Rnw file to elsarticle class

\documentclass{article}
\usepackage{multirow}
\usepackage{color,soul}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{caption}

\begin{document}
%\SweaveOpts{concordance=TRUE}

\makeatletter
\DeclareRobustCommand\bfseries{%
  \not@math@alphabet\bfseries\mathbf
  \fontseries\bfdefault\selectfont
  \boldmath % <-- added
}
\makeatother

@@

\section*{Abstract}

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.

@@

\section*{1. Introduction}

@@

\section*{3. Materials}

@@

\section*{5. Results and Discussion}

@@

  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data). Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{format(longest, big.mark = ",")} hours (\Sexpr{longest_d} days). Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.03 & 937.39  & <0.0001 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test Sets}     & 1.99 & 220.83  & <0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full Data}     & 2.03 & 1165.03 & <0.0001 & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}
\caption{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|l L{5.5cm}|c|c|}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.9346 (0.0476) & <0.0001 \\ 
                  & Camera & -0.3199 (0.0476) & \\ 
                  & Electronics & -0.0138 (0.0904)  & \\ 
                  & Game Console & 0.2458 (0.0784)  & \\ 
                  & Home & 0.3368 (0.0697) &  \\ 
                  & Other & -0.1304 (0.0555)  & \\ 
                  & PC & 0.2818 (0.0597) &  \\ 
                  & Tablet & -0.1566 (0.0815)  & \\ 
                  & Vehicle & 0.4056 (0.0695)  & \\
                  & Android/Other Phone (reference) & --- & \\ \hline
  \multicolumn{2}{|l|}{Weekend} & -0.1334 (0.0331)  & <0.0001 \\ \hline
  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.0247 (0.0499) & 0.6127 \\ \hline
  \multicolumn{2}{|l|}{Text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & <0.0001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.2571 (0.0332) &  <0.0001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.1069 (0.0364)  & 0.0031 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
\label{table:coefficients}
\end{table}

>>>>

\documentclass[preprint]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\usepackage{multirow}
\usepackage{color,soul}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{caption}

\begin{document}

% puts R2 in bold in table 3
\makeatletter
\DeclareRobustCommand\bfseries{%
  \not@math@alphabet\bfseries\mathbf
  \fontseries\bfdefault\selectfont
  \boldmath % <-- added
}
\makeatother

@@

\begin{frontmatter}
\title{Survival Analysis of Questions Posted on iFixit's Answers forum}

\author[cp]{L.K.~Oshita\corref{cor1}}
\cortext[cor1]{Corresponding author}
\ead{l.oshita@yahoo.com}

\author[ifixit]{A.~Pileggi}
\author[cp]{S.~Pileggi}

\address[cp]{California Polytechnic State University, San Luis Obispo, CA 93407, United States}
\address[ifixit]{iFixit, 1330 Monterey St, San Luis Obispo, CA 93401, United States}

\begin{abstract} 
Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.
\end{abstract}

\begin{keyword}
cox regression \sep response time \sep survival analysis \sep survival probabilty \sep Q\&A forum 
\end{keyword}

\end{frontmatter}

@@

\section{Introduction}

@@

\section{Materials}

@@

\section{Results and Discussion}

@@

  Of 8,025 questions in the full data, 7,760 were in English (97\% of the full data). Of those questions, \Sexpr{format(answered, big.mark = ",")} (\Sexpr{percentans}\%) received an answer by the download date. The shortest response time was \Sexpr{shortest} hours. The longest was \Sexpr{format(longest, big.mark = ",")} hours (\Sexpr{longest_d} days). Figure \ref{fig:answertimes} shows the distribution of response times for all questions analyzed.

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test Sets}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full Data}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}
\caption{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
\label{table:cv}
\end{table}

@@

% Final model on full data
\begin{table}[!htbp]
\centering
\begin{tabular}{|l L{5.5cm}|c|c|}
  \hline
 \textbf{Variable} & & \textbf{Coefficient (SE)} & \textbf{p-value} \\ \hline
  Device Category & Apple Product & 0.9346 (0.0476) & \textless0.0001 \\ 
                  & Camera & -0.3199 (0.0476) & \\ 
                  & Electronics & -0.0138 (0.0904)  & \\ 
                  & Game Console & 0.2458 (0.0784)  & \\ 
                  & Home & 0.3368 (0.0697) &  \\ 
                  & Other & -0.1304 (0.0555)  & \\ 
                  & PC & 0.2818 (0.0597) &  \\ 
                  & Tablet & -0.1566 (0.0815)  & \\ 
                  & Vehicle & 0.4056 (0.0695)  & \\
                  & Android/Other Phone (reference) & --- & \\ \hline
  \multicolumn{2}{|l|}{Weekend} & -0.1334 (0.0331)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|l|}{Text contains end punctuation} & 0.0247 (0.0499) & 0.6127 \\ \hline
  \multicolumn{2}{|l|}{Text is in all lower case} & -0.1770 (0.0645) &  0.0060 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among answered questions} & 0.0475 (0.0422) &  0.2596 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title contains terms considered frequently-used among unanswered questions} & -0.2808 (0.0340)  & \textless0.0001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Title ends in a question mark} & 0.2571 (0.0332) &  \textless0.0001 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User edited or added to the question's text after posting it} & 0.2983 (0.0857)  & 0.0005 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User was a member for less than one day before posting} & -0.1069 (0.0364)  & 0.0031 \\ \hline
  \multicolumn{2}{|L{9cm}|}{User made an effort to solve the problem prior to asking the question} & -0.0724 (0.0362)  & 0.0448 \\ \hline
  \multicolumn{2}{|L{9cm}|}{Square root of the average tag frequency} & 2.2609 (0.7196)  & 0.0020 \\ \hline
\end{tabular} 
\caption{Coefficients for predictors in the final model. (Continuous predictors fit with restricted cubic splines are not shown)} 
\label{table:coefficients}
\end{table}
